---
title: "Webinar 2 Survey Summary"
author: "Casey Wagnon"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: cosmo
    df_print: paged
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 8,
  fig.height = 6,
  fig.align = "center"
)
```

```{r packages, include=FALSE}
required_packages <- c(
  "tidyverse",
  "gt",
  "scales",
  "glue",
  "knitr"
)

installed <- rownames(installed.packages())
for (pkg in required_packages) {
  if (!pkg %in% installed) install.packages(pkg)
}

library(tidyverse)
library(gt)
library(scales)
library(glue)
library(knitr)
```

```{r source-analysis, include=FALSE}
source("summarize_webinar2_survey_report_ready.R", local = TRUE)
```

# Overview

This report summarizes responses from the Webinar 2 survey for the RGSM Options Tool. It includes participant information, response rates, closed-ended question summaries, plots for the choice questions, and tables of open-ended responses.

```{r overview-metrics}
overview_tbl <- tibble(
  Metric = c(
    "Total survey responses",
    "Unique participants",
    "Closed-ended questions summarized",
    "Open-ended questions summarized",
    "Two-option charts produced"
  ),
  Value = c(
    n_participants,
    nrow(participants_unique),
    length(closed_ended_cols),
    length(open_ended_cols_present),
    length(plot_list)
  )
)

gt(overview_tbl) |>
  tab_header(title = md("**Survey overview**"))
```

# Participant List

```{r participants-table}
gt(participants_unique) |>
  tab_header(title = md("**Participants**")) |>
  cols_label(
    first_name = "First name",
    last_name = "Last name",
    full_name = "Full name"
  )
```

# Response Rate by Question

```{r response-rate-table}
response_rate |>
  mutate(response_rate = percent(response_rate, accuracy = 0.1)) |>
  select(question_label, responses_non_missing, total_participants, response_rate) |>
  gt() |>
  tab_header(title = md("**Response rate by question**")) |>
  cols_label(
    question_label = "Question",
    responses_non_missing = "Responses",
    total_participants = "Total participants",
    response_rate = "Response rate"
  )
```

# Closed-Ended Question Summary

```{r closed-ended-wide}
summary_wide |>
  gt() |>
  tab_header(title = md("**Closed-ended question summary**"))
```

# Two-Option Question Plots

The plots below show counts and percentages for all two-option questions. 

```{r plot-loop, results='asis'}
for (nm in names(plot_list)) {
  cat("## ", get_label(nm), "\n\n", sep = "")
  print(plot_list[[nm]])
  cat("\n\n")
}
```

# Open-Ended Responses

```{r open-ended-intro, results='asis'}
if (nrow(open_ended_long) == 0) {
  cat("No open-ended responses were found in the uploaded file.")
}
```

```{r open-ended-sections, results='asis'}
for (q in open_ended_cols_present) {
  tab <- open_ended_long |>
    filter(question == q) |>
    select(full_name, response)

  cat("## ", get_label(q), "\n\n", sep = "")

  if (nrow(tab) == 0) {
    cat("No responses provided for this question.\n\n")
  } else {
    print(
      gt(tab) |>
        tab_header(title = md(paste0("**", get_label(q), "**"))) |>
        cols_label(
          full_name = "Participant",
          response = "Response"
        )
    )
  }

  cat("\n\n")
}
```

# Notes

- Percentages are based on non-missing responses for each question.
- Non-respondents: David Kitcheyan, Patrick Taber, Jenny Davis, Alison Hutson, and Reynalden Delgarito.
- No responses from the BIA.